Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-02-16 main.tex
added final comment on puzzles in resolution study. This is the end of this revision

%mm2
    {\bf [This appendix should be cited in the main paper]}
We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions for our high resolution simulations as compared to two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc. The physics in each of these simulations remains the same. However, our star formation algorithm is tied to resolution, since star formation proceeds in gas at densities where the Jeans mass becomes unresolved at the maximum resolution. A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.

@@

Finally, each of the lower resolution runs retain a surprisingly similar fractions of their produced metals in their disks (black curves in right panel of Figure~\ref{fig:resolution}), but this is about a factor of 2 below what is found in the fiducial run (5\% vs. 10\%). The amount that escapes the halo is significantly more, however. This is an interesting difference, as the resolution decrease primarily affects the disk of the galaxy; little to none of the halo volume is refined to the highest resolution, and so should be unaffected by this change. \textbf{I'm a bit puzzled by this difference...  }

>>>>

%mm2
    {\bf [This important appendix should be cited in the main paper, probably at least
once in the body and once in the conclusions.]}
We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions for our high resolution simulations as compared to two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc. The physics in each of these simulations remains the same. However, our star formation algorithm is tied to resolution, since star formation proceeds in gas at densities where the Jeans mass becomes unresolved at the maximum resolution. A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.

@@

Finally, each of the lower resolution runs retain a surprisingly similar fractions of their produced metals in their disks (black curves in right panel of Figure~\ref{fig:resolution}), but this is about a factor of 2 below what is found in the fiducial run (5\% vs. 10\%). The amount that escapes the halo is significantly more, however. This is an interesting difference, as the resolution decrease primarily affects the disk of the galaxy; little to none of the halo volume is refined to the highest resolution, and so should be unaffected by this change. \textbf{I'm a bit puzzled by this difference...  MM: Staring at Figure~\ref{fig:phase_resolution}, the key differences seem to be that at low resolution the locus of warm, presumably ionized gas at densities of $10^{-2}$ appears cooler, there's substantially less mass at $10^4$~K and extremely low densities, and substantially {\em more} mass at $10^6$~K, which is presumably what's carrying the metals out of the halo the low resolution runs.  Perhaps we are somehow not properly resolving adiabatic expansion in the plane or something like that??}
